The Name of the Title is Hope

### 2023-06-19 input/3_related_work.tex
introduction and prototype sections, working on related work

There is an ongoing debate, whether the temporal attraction is specific to intentional movements, or is more generally related to the perception between action and outcome

>>>>

There is an ongoing debate, whether the temporal attraction is specific to intentional movements, or is more generally related to the perception between action and outcome (Buhner 2012)
